### 2021-01-12 LaTeX-USENIX/sections/paper.tex
edits

\textbf{Gas.} Every transaction results in the participating nodes having to execute bytecode. This is not free. When a transaction is executed, each opcode in the execution path accrues a fixed, pre-specified amount of gas. The function caller will pledge to pay a certain amount of Ethereum's internal currency ETH (typically quoted in units of Gwei which is one billionth of an ETH) per unit of gas, and miners are free to choose to execute that transaction or ignore it. The function caller is charged for exactly the amount the transaction costs and they cap the maximum they are willing to be charged (\textit{gas limit})---if the cap is too low to complete the execution, the miner keeps the Gwei and reverts the state of the EVM (as if the function never ran).

@@

\paragraph{Refunds and PQs}

@@

The lesson here is that gas refunds incentivize developers to clean up storage variables they will not use again, but it is highly contextual as to whether it will pay for itself. Further the cap on the maximum refund means that refunds are not fully received for large cleanup operations (however removing the cap impacts the miners' incentives to include the transaction). This is a complicated and under-explored area of Ethereum in the research literature. For our own work, we strive to be good citizens of Ethereum and clean up to the extent that we can---thus all PQs in Table~\ref{tab:PQUnitTests} implement some cleanup and we select linked list with mapping and \texttt{DELETE} for \cm.

@@

\cm is proof of concept code. We try to simplify the design at every step to make it highly extensible but still functional without any extensions. A call market will open for a specified period of time during which it will accept a capped number of orders (parameterized so that all orders can be processed), and these orders are added to a PQ. Our vision (discussed below) is the market would be open for a very short period of time, close, and then reopen immediately (\eg every other block). We keep the design simple by not allowing cancellations which require a second transaction and front-running attacks apply to cancellation orders~\cite{eskandari2019sok}. As markets are relatively short-lived, orders simply expire when the market call period ends.

@@

\subsection{Security Analysis} \label{sec:front}

\paragraph{Front-running.}

@@

\subsection{Cleaning Up}

In \cm, traders preload their account with ERC-20 tokens and/or ETH. \cm tracks what they are owed using a mapping called \texttt{totalBalance} and allows traders to withdraw their tokens at any time. However if a trader submits an order (\ie ask for their tokens), the tokens are committed and not available for withdrawal until the market closes (after which, the tokens are either transferred to the buyer or, if the trade is not executed, returned to the trader). Committed tokens are also tracked in a mapping called \texttt{unavailableBalance}. Sellers can request a token withdrawal up to their total balance subtracted by their unavailable balance.

@@

 \textblue{ We need to find a home for this: another solution to reopen the market immediately after the closing call is to have many similar contracts for the market and  a factory contract to guide users to the correct address (from the reviewer's comment)}

As a module, we tried to keep \cm as simple as possible, and allow customizations and extensions as appropriate. We discuss potential modifications here.

>>>>

\textbf{Ethereum's Gas Model.} Every transaction results in the participating nodes having to execute bytecode. This is not free. When a transaction is executed, each opcode in the execution path accrues a fixed, pre-specified amount of gas. The function caller will pledge to pay a certain amount of Ethereum's internal currency ETH (typically quoted in units of Gwei which is one billionth of an ETH) per unit of gas, and miners are free to choose to execute that transaction or ignore it. The function caller is charged for exactly the amount the transaction costs and they cap the maximum they are willing to be charged (\textit{gas limit})---if the cap is too low to complete the execution, the miner keeps the Gwei and reverts the state of the EVM (as if the function never ran).

@@

\paragraph{Refunds and PQs.}

@@

The lesson here is that gas refunds incentivize developers to clean up storage variables they will not use again, but it is highly contextual as to whether it will pay for itself. Further the cap on the maximum refund means that refunds are not fully received for large cleanup operations (however removing the cap impacts the miners' incentives to include the transaction). This is a complicated and under-explored area of Ethereum in the research literature. For our own work, we strive to be good citizens of Ethereum and clean up to the extent that we can---thus all PQs in Table~\ref{tab:PQUnitTests} implement some cleanup.

@@

\cm is proof of concept code. We try to simplify the design at every step to make it an extensible base class but still functional without any extensions. A call market will open for a specified period of time during which it will accept a capped number of orders (\eg 100 orders---parameterized so that all orders can be processed), and these orders are added to a PQ. Our vision (discussed below) is the market would be open for a very short period of time, close, and then reopen immediately (\eg every other block). We keep the design simple by not allowing cancellations which require a second transaction and front-running attacks apply to cancellation orders~\cite{eskandari2019sok}. As markets are relatively short-lived, orders simply expire when the market call period ends.

@@

\subsection{Front-running} \label{sec:front}

@@

\subsection{Cleaning Up Revisted}

Beyond the cleaning up issues with priority queues, \cm also uses mappings with each market. Traders preload their account with ERC-20 tokens and/or ETH. \cm tracks what they are owed using a mapping called \texttt{totalBalance} and allows traders to withdraw their tokens at any time. However if a trader submits an order (\ie ask for their tokens), the tokens are committed and not available for withdrawal until the market closes (after which, the tokens are either transferred to the buyer or, if the trade is not executed, returned to the trader). Committed tokens are also tracked in a mapping called \texttt{unavailableBalance}. Sellers can request a token withdrawal up to their total balance subtracted by their unavailable balance.

@@

%\textblue{ We need to find a home for this: another solution to reopen the market immediately after the closing call is to have many similar contracts for the market and  a factory contract to guide users to the correct address (from the reviewer's comment)}

\cm is designed as base class that can be extended and customized. We discuss potential modifications here.
